---
title: "3D_spatial_network"
author: "Suraj Vidyadaran"
date: "Wednesday, December 23, 2015"
output: word_document
self_contained: no
---
###Data Description
This dataset was constructed by adding elevation information to a 2D road network in North Jutland, Denmark (covering a region of 185 x 135 km^2). Elevation values where extracted from a publicly available massive Laser Scan Point Cloud for Denmark (available at : [Web Link] (Bottom-most dataset)). This 3D road network was eventually used for benchmarking various fuel and CO2 estimation algorithms. This dataset can be used by any applications that require to know very accurate elevation information of a road network to perform more accurate routing for eco-routing, cyclist routes etc. For the data mining and machine learning community, this dataset can be used as 'ground-truth' validation in spatial mining techniques and satellite image processing. It has no class labels, but can be used in unsupervised learning and regression to guess some missing elevation information for some points on the road. 
The work was supported by the Reduction project that is funded by the European Comission as FP7-ICT-2011-7 STREP project number 288254. 

###Attribute Information

1. OSM_ID: OpenStreetMap ID for each road segment or edge in the graph. 
2. LONGITUDE: Web Mercaptor (Google format) longitude 
3. LATITUDE: Web Mercaptor (Google format) latitude 
4. ALTITUDE: Height in meters. 

Note: OSM_ID is the ID assigned by OpenStreetMaps ([Web Link]) to the road segments. Each (long,lat,altitude) point on a road segment (with unique OSM ID) is sorted in the same order as they appear on the road. So a 3D-polyline can be drawn by joining points of each row for each OSM_ID road segment.

###Data Cleaning and Exploratory Analysis
```{r}
spatial_network <- read.csv("F:/Analysis_Practice/Regression/3D_spatial_network/3D_spatial_network.txt", header=FALSE)

colnames(spatial_network)<-c("OSM_ID","longitude","latitude","altitude")

#Basic structure of the data
str(spatial_network)

#Summary of data
summary(spatial_network)

#Changing the ID into factors
spatial_network$OSM_ID<-as.factor(spatial_network$OSM_ID)
str(spatial_network)
```

###Data Analysis
```{r}
# Create a table of ID's
ID_table<-as.data.frame(table(spatial_network$OSM_ID))
ID_table<-ID_table[order(-ID_table$Freq),]
rownames(ID_table)<-NULL
colnames(ID_table)<-c("ID","Freq")
#Top 10 ids
top_ids<-ID_table[1:10,]
library(ggplot2)
 ggplot(top_ids,aes(x=reorder(ID,Freq),y=Freq,fill="ID"))+geom_bar(stat = "identity")+coord_flip()+xlab("OSM_ID")+ylab("Freq")+ggtitle("Top 10 OSM ID's")
```

```{r}
#Inspecting the altitude
library(ggplot2)
qplot(spatial_network$altitude,geom="histogram",fill=I("red"),col=I("black"),main="Histogram of Altitude",xlab="Altitude")
 below_0_altitude<-subset(spatial_network,spatial_network$altitude<0)
Above_100_altitude<-subset(spatial_network,spatial_network$altitude>100)

qplot(below_0_altitude$latitude,geom="histogram",fill=I("blue"),col=I("black"),main="Histogram of Latitude of below 0 altitudes",xlab="Latitude")

qplot(below_0_altitude$longitude,geom="histogram",fill=I("Yellow"),col=I("black"),main="Histogram of Longitude of below 0 altitudes",xlab="Longitude")

qplot(Above_100_altitude$longitude,geom="histogram",fill=I("Orange"),col=I("black"),main="Histogram of Longitude of Above 100 altitudes",xlab="Longitude")

qplot(Above_100_altitude$latitude,geom="histogram",fill=I("green"),col=I("black"),main="Histogram of Latitude of Above 100 altitudes",xlab="Latitude")

#Create a new Category for Altitudes
spatial_network$altitude_category<-NA
spatial_network$altitude_category[spatial_network$altitude<0]<-"Very Low"
spatial_network$altitude_category[spatial_network$altitude>0 & spatial_network$altitude<50]<-"Low"
spatial_network$altitude_category[spatial_network$altitude>50 & spatial_network$altitude<100]<-"High"
spatial_network$altitude_category[spatial_network$altitude>100]<-"Very High"

#Analysis of Category of altitudes
altitude_table<-as.data.frame(table(spatial_network$altitude_category))
colnames(altitude_table)<-c("Category","Freq")
ggplot(altitude_table,aes(x=Category,y=Freq,fill="Category"))+geom_bar(stat = "identity",position = "dodge",fill="violet")+geom_text(aes(label=Freq),size=5)
```


```{r,warning=FALSE,message=FALSE,echo=TRUE,cache=FALSE,results='asis',tidy=TRUE}
#Plotting on the Google Maps
library(googleVis)
spatial_network$latlon<-paste(spatial_network$latitude,spatial_network$longitude,sep=":")
map<-gvisMap(spatial_network,locationvar ="latlon",tipvar = "altitude_category",options=list(showTip=T,showLine=F,enableScrollWheel=TRUE,useMapTypeControl=TRUE,width=1400,height=800,allowHtml=TRUE) )
plot(map)
```

```{r}
#Plotting using plotGoogleMaps
library(plotGoogleMaps)

spatial2<-spatial_network[1:50000,]
coordinates(spatial2)<- ~ longitude+latitude
proj4string(spatial2) = CRS("+proj=longlat +datum=WGS84")
ic<-iconlabels(attribute = spatial_network$altitude_category,colPalette = rainbow(4),icon=TRUE,at=NULL,height=10,scale=0.6)
spatial3<-SpatialPointsDataFrame(spatial2,data = data.frame(ID=row.names(spatial2)))
m<-plotGoogleMaps(spatial3,filename = "myMap1.html",iconMarker = ic)
```
